Probabilities of polar aligned disks in binary star systems

### 2024-10-09 src/tex/ms.tex
Note Kozai fraction computed numerically
spelling

\RGM{However, for a massive disk, there are additional types of nodal precesion.... (describe) \citep{abod2022}.}

@@

For an isotropic angular momentum distribution,  the polar fraction in this limit is
\begin{equation}
    f_{{\rm polar}, j \gg 1} = \int_0^\pi\,\left (1-\frac{2}{\pi}\arcsin{\left (\sqrt{\frac{2}{5}} \csc{i} \right )}\right ) \sin{i}\,di = \variable{output/high_j_integral.txt}
\end{equation}
This is the value that the higher $j$ curves in Figure \ref{fig:ebin} tend to for low $e_{\rm b}$.

>>>>

\RGM{However, for a massive disk, there are additional types of nodal precession.... (describe) \citep{abod2022}.}

@@

For an isotropic angular momentum distribution,  the polar fraction in this limit is
\begin{equation}
    f_{{\rm polar}, j \gg 1} = \int_0^\pi\,\left (1-\frac{2}{\pi}\arcsin{\left (\sqrt{\frac{2}{5}} \csc{i} \right )}\right ) \sin{i}\,di = \variable{output/high_j_integral.txt}
\end{equation}
This is the value that the higher $j$ curves in Figure \ref{fig:ebin} tend to for low $e_{\rm b}$, computed numerically.
